### 2022-09-29 main/chapter_theory.tex
write abstract; quote tweaks; move higgs citation

Electromagnetic and weak forces are unified into the electroweak
interactions with four bosons $W^1$, $W^2$, $W^3$, and $B$ from the
$SU\!(2)_L$ and $U\!(1)$ symmetries respectively.
These would be massless if the symmetry were respected, but it is
`spontaneously' broken with the Higgs mechanism~\cite{
higgs1964broken,
englert1964broken
}%
\footnote{%
Historical accuracy prefers the name `Brout–Englert–Higgs mechanism', but
Peter~Higgs has reportedly suggested
``ABEGHHKtH mechanism''~\cite{close2011infinity}
to fully credit other associated work.%
}
which adds four scalar fields (as a complex doublet) with a potential that
moves the ground state to a gauge-\emph{asymmetric} configuration.
Around this new ground state, linear combinations of the electroweak fields
acquire masses while ``eating up''~\cite{rubakov1999classical} three of the
four scalar fields to yield the three weak bosons and the photon:
$W^1$ and $W^2$ mix into $W^+$ and $W^-$, while $W^3$ and $B$ mix into $Z$ and
$\gamma$.
The fourth scalar is the Higgs boson $h$~\cite{
glashow1959renorm,
weinberg1967model,
salam1959weak,
rubakov1999classical,
cottingham2007greenwood
}.

>>>>

Electromagnetic and weak forces are unified into the electroweak
interactions with four bosons $W^1$, $W^2$, $W^3$, and $B$ from the
$SU\!(2)_L$ and $U\!(1)$ symmetries respectively.
These would be massless if the symmetry were respected, but it is
`spontaneously' broken with the Higgs mechanism~\cite{
higgs1964broken,
englert1964broken
}%
\footnote{%
Historical accuracy prefers the name `Brout–Englert–Higgs mechanism', but
Peter~Higgs has reportedly suggested ``ABEGHHKtH mechanism'' to fully credit
associated work~\cite{close2011infinity}.%
}
which adds four scalar fields (as a complex doublet) with a potential that
moves the ground state to a gauge-\emph{asymmetric} configuration.
Around this new ground state, linear combinations of the electroweak fields
acquire masses while ``eating up''~\cite{rubakov1999classical} three of the
four scalar fields to yield the three weak bosons and the photon:
$W^1$ and $W^2$ mix into $W^+$ and $W^-$, while $W^3$ and $B$ mix into $Z$ and
$\gamma$.
The fourth scalar is the Higgs boson $h$~\cite{
glashow1959renorm,
weinberg1967model,
salam1959weak,
rubakov1999classical,
cottingham2007greenwood
}.

### 2022-09-29 main/frontmatter.tex
change from tabs to spaces; add frontmatter to contents with roman numbers
write abstract; quote tweaks; move higgs citation

\begin{abstract}
\TODO{searches for new effects in atlas are a core reason for its operations}

\TODO{this thesis presents such a search~\cite{atlas2022searches}}

\TODO{after briefly introducing its theoretical and experimental context}

\TODO{For given modelling of theory and experiment,
data analysis procedures dominate, and they take a very particular form
which we attempt to understand in its historical context
}

\TODO{
The result is compatible with many other observations,
that the Standard Model works very well at the LHC.
}

\TODO{supersymmetry is not falsifiable?}

\end{abstract}

@@

\begin{preface}
\begin{singlespacing}
\begin{epigraphs}
\qitem{%
Begin reading at Chapter N. Do \emph{not} read the quotations
that appear at the beginning of the chapter.%
}%
{Donald~E.~Knuth,
\textit{The Art of Computer Programming: Volume~1},
1975~\cite{knuth1975art}}
\end{epigraphs}
\end{singlespacing}

@@

\tableofcontents

>>>>

\begin{abstract}
To search for new phenomena is an essential endeavour of experimental physics,
and is enhanced by plausible theoretical predictions.
This thesis presents such a search \atlas\ data for signs of high-energy
protons scattering to massive resonances, whose dramatic decays are
predicted by supersymmetric models~\cite{atlas2022searches}.

Nothing new appears, and supports the Standard Model in its continuing
successful extrapolation to the describe the most extreme behaviours colliding
protons.
Supersymmetry as a concept as not falsified by these results,
nor by the many similar observations.
But it is not confirmed.

Data are best interpreted if their theoretical and experimental background is
understood, so this thesis begins by introducing the theoretical and
experimental background to its search,
and the subtleties of its data-analysis procedures in their historical context.
\end{abstract}

@@

\begin{preface}
\begin{singlespacing}
\begin{epigraphs}
\qitem{%
Begin reading at Chapter N. Do \emph{not} read the quotations
that appear at the beginning of the chapter.%
}%
{Donald~E.~Knuth,
\textit{The Art of Computer Programming, Volume~1},
1975~\cite{knuth1975art}}
\end{epigraphs}
\end{singlespacing}

@@

\afterpage{%
\phantomsection
\addcontentsline{toc}{chapter}{Contents}%
}
\tableofcontents
